\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-18 paper.tex
updated abstract

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism. Conventional testing approaches are ineffective in preventing serious but subtle bugs from reaching production. Formal techniques, such as the use of TLA+ in AWS~\cite{newcombe2015aws}, only verifies high level specification and falls short of checking executable code. In this paper, we present a new framework for testing distributed storage systems.
Our approach applies verification techniques for high-level specifications directly on the executable code and
significantly improves coverage of important system behaviors.

>>>>

\subsection*{Abstract}
Testing distributed systems is challenging due to multiple sources of nondeterminism. Conventional testing techniques are ineffective in preventing serious but subtle bugs from reaching production. Formal techniques, such as the use of TLA+ in Amazon Web Services, can only verify high-level specifications of systems at the level of logic-based models, and fall short of checking the actual executable code. In this paper, we present a new framework for testing distributed storage systems. Our approach applies systematic testing to thoroughly check that the executable code adheres to its high-level specifications, which significantly improves coverage of important system behaviors.
